\bf\mftitle

### 2011-03-01 doc/jInfer/projecttype/projecttype.tex
Documentation: ProjectType module: review round 1 part 2.

\begin{figure}
	\centering\includegraphics[scale=\myscale]{node_structure}
	\caption{Project directory structure} \label{node-structure}
\end{figure}

Each jInfer project type in NBP is after creation opened in project window and has some visual tree structure where each node in this tree is represented by NBP \code{Node} class. This structure is in jInfer project type provided by \code{JInferLogicalView} class that implements \code{LogicalViewProvider} interface from NBP and is available through \code{JInferProject} lookup. This class has one important method, \code{createLogicalView()} that returns instance of \code{RootNode} class of root node. Simple class structure is described in figure \ref{node-structure}.\\

\code{RootNode} extends NBP \code{AbstractNode} class which is basic implementation of NBP \code{Node}. This node contains four children nodes: three for input files (Document, Schema and Query) and one for output files generated by inference (Output). Root node also offers actions for adding input files, run inference and standard project actions like delete or move/rename project.\\

Each of the \emph{input} nodes is represented by \code{FolderNode} class and contains \emph{input file} nodes (represented by \code{FileNode} class) representing files added to the jInfer project. Notice that these \emph{input file} nodes represents files from filesystem and are not copied to the project folder structure. Because of this, if you delete this nodes from project tree, files from filesystem are not deleted.\\

\code{OutputNode} class represents \emph{Output} node in jInfer project type tree and is slightly different from \emph{input} nodes, because it refers to \emph{output} subfolder in project filesystem hierarchy. In other words, files contained in this folder are shown as sub-nodes in \emph{Output} node in project tree. This sub-nodes are represented by \code{OutputFileNode} class. Unlike \emph{input file} nodes, if you delete \emph{output file} node under the \emph{Output} node, file represented by this node is also deleted from filesystem.

@@

Each node in project tree hierarchy contains set of actions available from its context menu. Besides standard actions for root node or file node, jInfer project type introduce its own actions. These actions could be separated into three groups: actions for \emph{root} node, actions for \emph{input folder} nodes and one action for \emph{input/output file} nodes implemented by \code{ValidateAction} class. All classes implementing some jInfer project action extend standard java \code{javax.swing.AbstractAction} class besides \code{ValidateAction} class which is described in \ref{validate-action}.\\

@@

This group contains two actions, first is action that allows adding input files into \emph{input folder} nodes (implemented by \code{FilesAddAction} class). Second one is slightly different, because unlike from the previous action, this one doesn't create new item in \emph{root} node context menu but implements functionality for item that already exists in context menu - Run action.\\

First of the two actions, after its invocation, file choose dialog is opened which has set file filter according to available classes that implement \code{Processor} interface registered in jInfer with \code{ServiceProvider}. After selecting files in dialog, these files are inserted into particular \emph{input folder} node according to mapping of file extension to folder type gained from \code{Processor} classes. If no mapping for some extension exists, this file is inserted into folder which is defined in \emph{Miscellaneous} properties category (section \ref{pref}).\\

Run action, which is available in root node context menu, is also present in NBP toolbar as a \emph{Run} button and in jInfer Welcome window. This action is implemented in \code{RunAction} class and simply invokes \jmodule{Runner}s \code{run()} method, if no other inference is already running, otherwise information dialog pops up, informing about already running inference. This check is done with \code{setActiveProject()} from \code{RunningProject} class (section \ref{running-project}).

@@

To this group of actions belong two actions: action for adding input files into \emph{input folder} node (\code{FileAddAction} class) and action for deleting all input files in \emph{input folder} node (\code{DeleteAllAction} class). \code{FileAddAction} class implements action which opens file choose dialog and selected files are added into particular \emph{input folder} node. \code{DeleteAllAction} class simply removes all input files previously added into particular \emph{input folder} node.

\subsubsection{ValidateAction class}\label{validate-action}

\code{ValidateAction} class implements action, which allows documents and schema files to be validated against each other. Because of this, action is presented in context menu of document and schema files (in actual implementation is available for XML, dtd and XML schema files). Unlike the other action classes, this extends NBP \code{NodeAction} class, which allows to enable/disable action in context menu according to node selection. Action is enabled only if exactly one schema file is selected and one or more XML files. If the selected XML files are valid against selected schema, information dialog is popped up, otherwise error dialog is popped up and in \emph{validate} output window is printed error message describing cause of non-validity XML files against schema.\\

For the validation against XML Schema, we use standard Java validation API \cite{xml_validate}. Besides XML Schema, this API allows to  validate XML also against \emph{Relax NG} and \emph{Schematron} schema. If you want to extend the functionality of one of these schemas, you need to set \code{schemaLanguage} local variable to appropriate \code{XMLConstant}. If you need to extend validation to some other type of schema, you can use dtd validation as a sample.\\

For a validation error handling is used \code{JInferErrorHander} class which extends \code{DefaultHandler} class and overrides \code{error()} and \code{fatalError()} methods from this class. In these methods is created error message, which is consequently printed in validation \emph{output} window.

>>>>

\begin{figure}
	\centering\includegraphics[scale=\myscale]{node_structure}
	\caption{Project nodes structure} \label{node-structure}
\end{figure}

Each jInfer project in NBP is open after its creation in the Projects view and has tree structure where each node is represented by a NBP \code{Node} class. This structure in jInfer project type is provided by the \code{JInferLogicalView} class implementing \code{LogicalViewProvider} interface from NBP and is available through the \code{JInferProject} lookup. This class has one important method: \code{createLogicalView()} returning an instance of \code{RootNode} class. Simple class structure is described in figure \ref{node-structure}.\\

\code{RootNode} extends NBP \code{AbstractNode} class which is a basic implementation of NBP \code{Node}. This node contains four children nodes: three for input files (Document, Schema and Query) and one for output files generated by the inference (Output). Root node also offers actions for adding input files, inference running and standard project actions like delete or move/rename project.\\

Each of the \emph{input} nodes is represented by a \code{FolderNode} class and contains \emph{input file} nodes (represented by a \code{FileNode} class) representing files added to the jInfer project. Notice that these \emph{input file} nodes represent existing files in the filesystem and are not copied to the project folder structure. Because of this, if you delete these nodes from project tree, files in the filesystem are not affected.\\

\code{OutputNode} class represents an \emph{Output} node in jInfer project type tree and is slightly different from \emph{input} nodes, because it refers to \emph{output} subfolder in project filesystem hierarchy. In other words, files contained in this folder are shown as subnodes in \emph{Output} node in project tree. These subnodes are represented by \code{OutputFileNode} class. Unlike \emph{input file} nodes, if you delete \emph{output file} node under the \emph{Output} node, file represented by this node is deleted from filesystem too.

@@

Each node in jInfer project tree hierarchy contains a set of actions available from its context menu. Besides standard NBP actions for root node or file node, jInfer project type introduces its own actions. These actions can be divided into three groups: actions for \emph{root} node, actions for \emph{input folder} nodes and one action for \emph{input/output file} nodes implemented by \code{ValidateAction} class. All classes implementing a jInfer project action extend standard java \code{javax.\.swing.\.AbstractAction} class besides \code{ValidateAction} class which is described in \ref{validate-action}.\\

@@

This group contains two actions: an action that allows adding input files into \emph{input folder} nodes (implemented by \code{FilesAddAction} class). Second one is slightly different, because it implements functionality for an item that already exists in context menu - Run action.\\

After invoking the first of the two actions, a file chooser dialog is open. Its file filter is set according to available classes implementing \code{Processor} interface registered in jInfer with \code{ServiceProvider}. After selecting file(s) in dialog, these files are inserted into the particular \emph{input folder} node according to mapping of their file extensions to folder type retrieved from \code{Processor} classes. If no mapping for some extension exists, this file is inserted into a default folder defined in \emph{Miscellaneous} properties category (section \ref{pref}).\\

Run action, available from root node context menu, is also present in NBP toolbar as a \emph{Run} button and in jInfer Welcome window. This action is implemented in \code{RunAction} class and simply invokes \jmodule{Runner}'s \code{run()} method, if no other inference is already running. Otherwise an information dialog pops up, informing about the already running inference. This check is done invoking the \code{setActiveProject()} from \code{RunningProject} class (section \ref{running-project}).

@@

Two actions belong to this group: action for adding input files into \emph{input folder} node (\code{FileAddAction} class) and action for deleting all input files in the \emph{input folder} node (\code{DeleteAllAction} class). \code{FileAddAction} class implements action which opens a file chooser dialog and adds the selected files into the particular \emph{input folder} node. \code{DeleteAllAction} class simply removes all input files previously added into that particular \emph{input folder} node.

\subsubsection{ValidateAction}\label{validate-action}

\code{ValidateAction} class implements action that allows documents and schema files to be validated against each other. Because of this, action is presented in context menu of document and schema files (its actual implementation is available for XML, DTD and XML Schema files). Unlike the other action classes, this extends NBP \code{NodeAction} class, which allows to enable/disable the action in context menu according to node selection. Action is enabled only if exactly one schema file and one or more XML files are selected at the same time. If the selected XML files are valid against selected schema, information dialog pops up, otherwise error dialog pops up and an error message describing the cause of non-validity of XML files against this schema is printed in \emph{validate} output window.\\

For the validation against XML Schema, we use standard Java validation API \cite{xml_validate}. Besides XML Schema, this API allows to validate XML also against \emph{Relax NG} and \emph{Schematron} schema. If you want to extend the functionality of one of these schemas, you need to set \code{schemaLanguage} local variable to appropriate \code{XMLConstant}. If you need to extend validation to some other type of schema, you can use DTD validation as an example.\\

For validation error handling the \code{JInferErrorHander} class is used. It extends \code{DefaultHandler} class and overrides its \code{error()} and \code{fatalError()} methods. In these methods an error message is created, which is consequently printed in validation \emph{output} window.
